Multiple Linear Regression on Sleep Data

### 2025-05-05 paper/paper.qmd
working outlier and multicoll

```{r}
full_model <- lm(sleep_duration ~ ., data = sleep)

model_summary <- summary(full_model)

model_stats <- tibble::tibble(`F-statistic` = round(model_summary$fstatistic[1], 2),
                              `Adjusted R²` = round(model_summary$adj.r.squared, 3),
                              `Residual Sum of Squares` = round(sum(residuals(full_model)^2), 2),
                              `Total Sum of Squares` = round(sum((sleep$sleep_duration - mean(sleep$sleep_duration))^2), 2))

@@

>>>>

```{r}
full_model <- lm(sleep_duration ~ ., data = sleep)
full_model_summary <- summary(full_model)

model_stats <- tibble::tibble(`F-statistic` = round(full_model_summary$fstatistic[1], 2),
                              `Adjusted R²` = round(full_model_summary$adj.r.squared, 3),
                              `Residual Sum of Squares` = round(sum(residuals(full_model)^2), 2),
                              `Total Sum of Squares` = round(sum((sleep$sleep_duration - mean(sleep$sleep_duration))^2), 2))

@@

```{r}
kable(vif(full_model))
```
